Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-19 paper/paper.tex
Despecificify

Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
specific branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
set of variables already assigned to values different from $\bot$. The next variable to be assigned
is chosen within the set of non assigned variables which are the neighbour of at least one vertex of
$\mathit{CComp}$.  When this set is empty, all remaining non assigned variables are assigned to
$\bot$. We illustrate this in \cref{figure:restricted}.

@@

\Cref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by
specific branching (Branch), by specific filtering (Filter), or by combining specific branching and
filtering (Both). We show only results using the best variant for each class---that is, MAC for
labelled graphs, and FC for unlabelled graphs (the other results are very similar).  On labelled
graphs, we see many instances which are solved by branching but not filtering, and vice versa.
However, combining both is rarely much worse than just doing one or the other, and is often much
better, even if on average it is slightly slower.  On unlabelled graphs, we observe that the three
variants have rather similar performance.

>>>>

Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} implement the connectedness constraint by using a
branching rule which selects the next variable to be assigned. Let $\mathit{CComp}$ be the
set of variables already assigned to values different from $\bot$. The next variable to be assigned
is chosen within the set of non assigned variables which are the neighbour of at least one vertex of
$\mathit{CComp}$.  When this set is empty, all remaining non assigned variables are assigned to
$\bot$. We illustrate this in \cref{figure:restricted}.

@@

\Cref{figure:connected-cp} compares the three approaches for ensuring connectedness in CP: by
branching (Branch), by filtering (Filter), or by combining branching and
filtering (Both). We show only results using the best variant for each class---that is, MAC for
labelled graphs, and FC for unlabelled graphs (the other results are very similar).  On labelled
graphs, we see many instances which are solved by branching but not filtering, and vice versa.
However, combining both is rarely much worse than just doing one or the other, and is often much
better, even if on average it is slightly slower.  On unlabelled graphs, we observe that the three
variants have rather similar performance.
